Convex Surrogates via Polyhedral Losses

### 2019-05-14 neurips-19/poly-embed.tex
Jessie added examples and took an iteration of proofs

\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...  I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
\jessie{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.  We might also assume our discrete loss is nonnegative?}

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, the hinge loss is polyhedral, whereas logistic loss is not.

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}

  First, suppose $L$ embeds $\ell$.
  We want to show that for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Fix $p \in \simplex$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then 
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$, thus this case cannot happen.

  \jessie{Slightly stuck here.  Will revisit, but just FYI.}
  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
  Let $F$ be the set of facets in $\risk{\ell}$.
  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.  My inclination is to show there's the ``stripped'' loss that we embed ($\varphi(u) = u$) and for any bijection $\phi$, we can see that $\ell$ can be modified to $\ell^\phi$ so that $\risk{\ell} = \risk{\ell^\phi}$, and $L$ also embeds $\ell^\phi$ with $\varphi(r) = \phi(r)$.  Does that make sense?}

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral. \jessie{Need to prove?}
  Therefore, $\risk{L}$ is polyhedral.

  For the reverse implication, suppose $\risk{L}$ is polyhedral. 
  For each facet $f$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
  (Note that this $u$ will be unique regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ \jessie{add that $F$ is full set of facets} is finite.
  Now define the discrete loss $\ell(r,y) = L(r,y)$ for all $r \in \R$.

  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
  For all $p \in \simplex$, we observe
  \begin{align*}
  	\risk{L} = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}
  \end{align*}
  \jessie{Probably want to rigorously flesh out argument for the second equality.}
  Thus, $L$ embeds the discrete $\ell$ as constructed.

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}
  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
  \jessie{$L$ polyhedral implies $L^* = -\risk{L}$ polyhedral (cite?) implies $\risk{L}$ polyhedral.}
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proving (in)consistency via embeddings}
The above techniques allow us to evaluate and simplify some previous historical results.
For example, Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.
They then create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
In particular, they evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analysis}, one of which is shown to be convex, but they leave its consistency as an open question.

After our discussion of embeddings, it is worth noting that we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ if and only if $L$ embeds $\ell$.
Therefore, we can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent by showing the discrete loss that their loss embeds is not the discrete loss measuring top-$k$ error.

In particular, we measure top-$k$ error by 
\begin{align}
\ell_{top-k}(r,y) &= 
\begin{cases}
0 & r_y = 1 \text{ and } \|r \|_{\infty} \leq k\\
1 & \text{otherwise}
\end{cases}
\end{align}
Where $r \in 2^n$ can be thought of as a binary vector representing set inclusion and $k \leq n$ is a constant.

Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
Following the numbering of Yang and Koyejo, we call the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$.

It can be verified that $\ell_2(r,y) = \begin{cases}
\min\left(\frac{HD(r, e_y)}{k}, 1\right) & s_y = 1 \\
1 + \min \left(\frac{HD(s, \vec{0})}{k}, 1\right) & s_y = 0
\end{cases}$, where $HD(\cdot, \cdot)$ is the Hamming distance between two vectors.

@@

\jessie{Lovasz hinge paper? ~\cite{yu2018lovasz}}

@@

\raf{ACKNOWLEDGEMENTS (commented out for submission)}
% \subsection*{Acknowledgements}
% We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
% Arpit
% NSF grant
\bibliographystyle{plainnat}
\bibliography{diss,extra}

@@

\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
  Let $L:\reals^d\to\reals_+$ \jessiet{$\reals_+^\Y$?} be a polyhedral loss.
  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant \jessiet{over $p$} whenever $p\in\inter\simplex$.
  Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
  By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.

@@

  Now define $L:\reals^n\to\reals^\Y$ \jessiet{$\to \reals_+^\Y$} by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
  \jessiet{Geometrically, what does this look like?  I'm imagining it as our tipping cost function, but I'm not sure on that.}
  We will show that $L$ embeds $\gamma$.
  As $L$ is convex, we may write the optimality condition as
  \begin{equation}
    \label{eq:2}
    u \in \prop{L}(p) \iff u \in \argmin_{u'} \inprod{p}{L(u')} \iff 0 \in \partial \inprod{p}{L(u)}~,
  \end{equation}
  where the subgradient $\partial$ is with respect to $u$.
  Plugging in our definition of $L$, we have
  \begin{align*}
    0 \in \partial \inprod{p}{L(u)}
    & \iff 0 \in \partial \inprod{p}{\left(C(u)\ones - u\right)}
    \\
    % & \iff 0 \in \partial \left(C(u) - p\cdot u\right)
    % \\
    & \iff 0 \in \partial C(u) - \{p\}
    \\
    & \iff p \in \partial C(u)~.
  \end{align*}
  \jessiet{Not sure I see this- REVISIT.}

>>>>

\raf{Important TODO: we use $\reals^\Y$ sometimes and $\reals^\Y_+$ other times; ideally both $+$, but we need to see what we can prove...  I know this is a key detail for polyhedral losses, to ensure the inf is always attained.}
\jessiet{If the convex loss is bounded from below by $M$, we can say $\reals^\Y_+$ WLOG since $L$ elicits $\Gamma$ implies $(L +c)$ elicits $\Gamma$ for any constant $c$-- in particular, $M$.  We might also assume our discrete loss is nonnegative?}

@@

Most of the surrogates $L$ we consider will be \emph{polyhedral}, meaning piecewise linear and convex\jessiet{and bounded from below?}; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is a \emph{polyhedral} if $L(u)_y$ is a polyhedral (convex) function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, the hinge loss is polyhedral, whereas logistic loss is not.

@@

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raf{Use distributions on the interior of the cells; since the risk is differentiable there, the loss is uniquely defined, and thus the same, and the same throughout the cell.}
  \jessie{Alluded to in COLT Lemma 11 and Prop 12 (Lemma~\ref{lem:finite-full-dim} and Prop~\ref{prop:embed-trim} here), but I don't see us prove this in the original paper.}

  \jessie{The forward implication is a corollary of COLT Lemma 11}

  %Jessie's first attempt at a proof
  First, suppose $L$ embeds $\ell$, and fix $p \in \simplex$.
  We want to show that for all $p \in \simplex$ that $\inf_{u\in\reals^d} L(u,p) = \min_{r \in \R} \ell(r, p)$.
  Consider two cases: first suppose there exists a $u \in \reals^d$ so that $u \in \arginf_{u' \in \reals^d}L(u',p)$ and $u \in \varphi(\R)$.
  Then 
  \begin{align*}
  \inf_u L(u,p) = \min_{r \in \R} L(\varphi(r), p) = \min_{r \in \R} \ell(r, p)
  \end{align*}
   first by the case assumption and then by the definition of embedding.
  Now in the second case, if such a $u$ does not exist, then $\inf_{u \in \reals^d}L(u,p) < \min_r L(\varphi(r), p) = \min_r \ell(r,p)$.
  Therefore, $r \in \argmin_r' \ell(r', p) \implies \varphi(r) \not \in \argmin_u L(u,p)$ which contradicts the assertion that $L$ embeds $\ell$.

  \jessie{Not sure on this one, just FYI.  I think it's a corollary of COLT Prop 12, now Prop~\ref{prop:embed-trim}.}
  Now, to see that $\risk{\ell} = \risk{L} \implies L$ embesds $\ell$, consider $F$ to be the set of facets of the loss of $\risk{L}$.
  For each facet $f \in \F$, we know by nonredundancy that there is some $p \in \inter{f}$ so that $\risk{L}$ is differentiable at $p$.
  Moreover, by Frongillo and Kash~\jessie{CITE... 2014 paper? Theorem 24?} we know that both $\ell$ and $L$ have a unique minimizer at $p$, and since the subgradients of the risks are the same (by their equality), we know the minimizers of the losses are also the same.
  Therefore, we can see (with more elaboriating) that $L$ embeds $\ell$.

%  Now let us show that $\risk{L} = \risk{\ell} \implies L$ embeds $\ell$.
%  Let $F$ be the set of facets in $\risk{\ell}$.
%  For each $f \in F$, there is some $p \in \inter{f}$ so that $\risk{L}(p) = \risk{\ell}(p)$ is differentiable, and so the loss $L$ must then be uniquely defined.
%  \jessie{This is my interpretation of your note, but I don't see how this proves the existence of an embedding.  My inclination is to show there's the ``stripped'' loss that we embed ($\varphi(u) = u$) and for any bijection $\phi$, we can see that $\ell$ can be modified to $\ell^\phi$ so that $\risk{\ell} = \risk{\ell^\phi}$, and $L$ also embeds $\ell^\phi$ with $\varphi(r) = \phi(r)$.  Does that make sense?}

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  \jessie{My attempt below}
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, we know that $\risk{\ell}$ is polyhedral. \jessie{Need to prove? Stated as fact in proof of COLT Prop 12...}
  Therefore, $\risk{L}$ is polyhedral.

  For the reverse implication, suppose $\risk{L}$ is polyhedral. 
  For each facet $f \in F$ of $\risk{L}$, consider the report $u_f = \arginf_{u'} L(u', p)$ for some $p \in \inter f$.
  (Note that this $u$ will be unique regardless of the choice of $p\in \inter f$, since $\risk{L}$ is differentiable here.)
  Since $\risk{L}$ has a finite set of facets, the set $\R = \{u_f\}_{f \in F}$ \jessie{add that $F$ is full set of facets} is finite.
  Now define the discrete loss $\ell:\R \to \Y$ by $\ell(r,y) = L(r,y)$.

  To see that $L$ embeds this discrete $\ell$, consider the embedding function to be the identity for all $r \in \R$.
  By Proposition~\ref{prop:embed-bayes-risks}, it is sufficient to show $\risk{L} = \risk{\ell}$.
  For all $p \in \simplex$, we observe
  \begin{align*}
  	\risk{L}(p) = \inf_{u \in \reals^d} L(u,p) = \min_{r \in \R} L(r,p) = \min_{r \in \R} \ell(r, p) = \risk{\ell}(p)
  \end{align*}
  Note that the second equality holds because for every $p \in \simplex$, we know there is some $r \in \R$ such that $r \in \arginf_u L(u,p)$ by closure of subgradient sets, and thus the loss values are the same, regardless of if we restrict to $\R$ or stay in $\reals^d$.
  Thus, $L$ embeds the discrete $\ell$ as constructed.

@@

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}
  We merely show $L$ polyhedral $\implies$ $\risk{L}$ polyhedral, and apply Proposition~\ref{prop:embed-risk-poly}.
  \raf{Not sure how trivial this is, but it's definitely true.  I suspect it has a very short proof.}
  \jessie{$L(u,p)$ polyhedral in $\reals^d$ implies $L^*(0,p) = -\risk{L}(p)$ polyhedral in $\simplex$ implies $\risk{L}$ polyhedral.
  Now we can apply Proposition~\ref{prop:embed-risk-poly} to observe the result.}

  \jessie{Can also show that $L$ embeds $L|_\R$ like the original paper and use a modification of COLT Lemma 11.}
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proving (in)consistency via embeddings}
The above techniques allow us to evaluate and simplify some previous results in the literature.
\subsection{Top-$k$ loss}
Yang and Koyejo~\cite{yang2018consistency} prove the inconsistency of a family of surrogates for the top-$k$ classification problem.

The top $k$ classification problem takes as input a vector $u \in \reals^n$, and observes outcome $y \in [n]$.
The input is sorted in descending order, and the function $t_k(u)$ yields a set of outcomes associated to the first $k$ elements of this sorted input.
For example, if $u = (4,1,2)$, then $t_k(u) = \{0,2\}$ for the first and third outcomes.

We say the top-$k$ loss is
\begin{align}
\ell_{top-k}(u,y) = \begin{cases}
0 & y \in t_k(u)\\
1 & \text{otherwise}
\end{cases}
\end{align}

Yang and Koyejo~\cite{yang2018consistency} create a new surrogate loss that is consistent for the top-$k$ problem, although it should be noted that their surrogate is not convex.
In particular, Yang and Koyejo evaluate two losses given by Lapin et al.~\cite{lapin2016loss, lapin2018analsis}, one of which is shown to be convex, but its consistency is left as an open question.

After our discussion of embeddings, we now have a way of proving consistency: a surrogate $L$ is consistent with respect to a discrete loss $\ell$ \jessie{we still haven't defined consistency... here I'm going by Yang's consistency.  I suppose we still need a proof of this.} if and only if $L$ embeds $\ell$.
We can then prove that the surrogates given by Lapin et al.~\cite{lapin2018analysis} are not consistent in a more suffice manner; we do so by showing the discrete loss that their surrogate embeds is not equal to  $\ell_{top-k}$.

Here, $r \in 2^n$ can be thought of as a binary 0-1 vector representing set inclusion and $k \leq n$ is a constant.
There is some ambiguity on how $t_k(r)$ should be defined if $\|r \|_\infty > k$, so we shall say that $y \not \in t_k(r)$ in such instances.

Now, for example, consider the surrogate discussed by Lapin et al.~\cite{yang2018consistency}, and Yang and Koyejo~\cite{yang2018consistency}.
Following the numbering of Yang and Koyejo, we call the surrogate $L_2(u,y) := \max\left( \frac{1}{k} \sum_{i=1}^k (u + \indopp(y))_{[i]} - u_y \right) $, where $\indopp(y) = \ones - e_y$, and $(x)_{[i]}$ is the $i^{th}$ largest component of $x$.

It can be verified that 
$\ell_2(r,y) = \begin{cases}
\min\left(\frac{HD(r, e_y)}{k}, 1\right) & r_y = 1 \\
1 + \min \left(\frac{HD(s, \vec{0})}{k}, 1\right) & r_y = 0
\end{cases}$,
 where $HD(\cdot, \cdot)$ is the Hamming distance between two vectors.

@@

\subsection{Lov\'asz Hinge}
\jessie{Lovasz hinge paper? ~\cite{yu2018lovasz}}

\subsection{Abstain loss}
Our final example of an embedded loss is given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
In their work, they provide a consistent, polyhedral \jessie{?} surrogate for the abstain loss $\ell_{abs_{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
\begin{align}\label{eq:abstain}
\ell_{abs_{\alpha}}(r,y) := \begin{cases}
0 & r = y\\
\alpha & r = a\\
1 & otherwise
\end{cases}
\end{align}
Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.

The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
They go on to show consistency and provide a \jessie{which type?} link function from their surrogate to $\ell_{abs_{1/2}}$.

@@

\raf{ACKNOWLEDGEMENTS (commented out for submission)}
% \subsection*{Acknowledgements}
% We thank Peter Bartlett for several discussions early on, which led to a proof of \raf{1-d reduction} among other insights.
% Arpit
% Eric Balkanski for a proof of \raf{Lemma on submodularity}
% NSF grant
\bibliographystyle{plainnat}
\bibliography{diss,extra}

@@

\begin{proof}[Proof of Theorem~\ref{thm:polyhedral-embed}]
  Let $L:\reals^d\to\reals_+$ \jessiet{$\reals_+^\Y$?} be a polyhedral loss.
  For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
  From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant over $p$ whenever $p\in\inter\simplex$.
  Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
  By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.

@@

  Now define $L:\reals^n\to\reals_+^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
  \jessiet{Geometrically, what does this look like?  I'm imagining it as our tipping cost function, but I'm not sure on that.}
  We will show that $L$ embeds $\gamma$.
  As $L$ is convex, we may write the optimality condition as
  \begin{equation}
    \label{eq:2}
    u \in \prop{L}(p) \iff u \in \argmin_{u'} \inprod{p}{L(u')} \iff 0 \in \partial \inprod{p}{L(u)}~,
  \end{equation}
  where the subgradient $\partial$ is with respect to $u$.
  Plugging in our definition of $L$, we have
  \begin{align*}
    0 \in \partial \inprod{p}{L(u)}
    & \iff 0 \in \partial \inprod{p}{\left(C(u)\ones - u\right)}
    \\
    % & \iff 0 \in \partial \left(C(u) - p\cdot u\right)
    % \\
    & \iff 0 \in \partial C(u) - \{p\}
    \\
    & \iff p \in \partial C(u)~.
  \end{align*}
  \jessiet{Not sure I see this- REVISIT.}
